Title

### 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Adding to the tex presentation new figures

\hspace{4cm}   between 6 -12 quarters

@@

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_15_06_45}
\end{figure}

@@

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_15_06_52}
\end{figure}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{FEV of TFP explained by the two shocks at 40 periods}

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
		 & 0.37195 & 0.43944 & 0.81138 \\
		\hline
	\end{tabular}
\end{large}

>>>>

\hspace{4cm}   between 6-12 quarters

@@

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_36}
\end{figure}

@@

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_47}
\end{figure}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{FEV explained by the two shocks at 40 periods}

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
	GDP            &         &        &         \\
	Cons           &         &        &         \\
		\hline
	\end{tabular}
\end{large}
